The universal property of direct integrals in W$^*$-categories

### 2018-11-30 direct_integrals.tex
Direct sums draft now separate

\begin{ex}
$\NRep{\cat{N}}$ has a canonical measurable structure of this kind if we declare a collection of objects $\mathcal{S}$ to be measurable if for every Hilbert space $\H$, the set of all $\pi : \cat{N} \to \B{\H}$ which are in is $\mathcal{S}$ is measurable, in the sense of the smallest $\sigma$-algebra which makes the evaluation maps $\pi \mapsto \langle \xi,\pi(a) \xi\rangle$ for $\xi\in\H$ and $a\in\cat{N}$ measurable. As a degenerate special case, for $\cat{C} = \Hilb$ we obtain the discrete $\sigma$-algebra on the objects.

@@

@@

>>>>

\newcommand{\Calg}{\mathcal{A}}

\begin{ex}
\label{nrep_measurable}
Let $\Calg$ be a C$^*$-algebra. Then $\Rep{\Calg}$ has a canonical measurable structure of this kind, which we describe in the following. First, a collection of representations $\mathcal{S}$ on a fixed Hilbert space $\H$ is measurable if it is in the smallest $\sigma$-algebra which makes the evaluation maps $\pi \mapsto \langle \xi,\pi(a) \xi\rangle$ for $\xi\in\H$ and $a\in\Calg$ measurable. Furthermore, we equip $\Obj{\Hilb}$ with the countable-cocountable $\sigma$-algebra. On $\Obj{\Rep{\Calg}}$, we hence put the $\sigma$-algebra consisting of countable or cocountable unions of measurable subsets of $\{ \pi : \cat{N} \to \B{\H} \}$ for varying $\H$.

As a degenerate special case, for $\cat{C} = \Hilb$ we obtain the discrete $\sigma$-algebra on the objects.

@@

\begin{ex}
In the situation of Example~\ref{nrep_measurable}, a family of representations $x \mapsto (\H_x,\pi_x)$ is measurable if and only if the following holds: there is a countable measurable partition $X = \coprod_{n\in\N} X_n$, such that $x\mapsto \H_x$ is constant on each part $X_n$, and such that on each part $X_n$, the function $x \mapsto \pi_x$ is measurable.

More concretely, let us consider $\Rep{C(S^1)}$ and $X := S^1$, equipped with its usual $\sigma$-algebra and measure (the normalization is irrelevant). To every $x\in X$ we assign the Hilbert space $\C$, together with the unitary given by multiplication by $x$. This induces a representation of $C(S^1)$ as usual via functional calculus, which in this case simply corresponds to function evaluation at $x\in S^1$. Measurability of the function $x\mapsto \pi_x$ amounts to measurability of each map $x\mapsto \langle\xi,\pi(a)\xi\rangle$ for $\xi\in\C$ and $a\in C(S^1)$, or equivalently measurability of $x\mapsto |\xi|^2 a(x)$, which is obvious.
\end{ex}

@@

\begin{defn}
A \emph{normed set} $(S,\|\cdot\|)$ is a set $S$ together with a map $\|\cdot\| : S\to \R_+$.
\end{defn}

\begin{defn}
Given a W$^*$-category $\cat{C}$, an \emph{affiliated morphism} $f : A\to B$ is a transformation
\[
	J \to \cat{C}(-,B),
\]
where $J\subseteq\cat{C}(-,A)$ is a sieve that is locally ultraweakly dense.
\end{defn}

Affiliated morphisms generalize unbounded operators. If $f : A \to B$ is an affiliated morphism and $g : B\to C$ a genuine morphism, then we can form the composition $gf$. Precomposing by a genuine morphism is not possible in general, since the pullback sieve need not be locally ultraweakly dense.

\newcommand{\aff}{\mathrm{aff}}

\begin{defn}
A \emph{W$^*$-category with affiliated morphisms} is a W$^*$-category together with a set $\cat{C}_\aff(A,B)$ of affiliated morphisms for every two objects $A,B\in\cat{C}$.
\end{defn}

\tob{This terminology may not be very good, since affiliated operators still seem to have a reasonable functional calculus}

\begin{ex}
We consider $\Hilb$ as a W$^*$-category with affiliated morphisms. These correspond to the unbounded operators modulo equivalence.

Let $\Calg$ be a C$^*$-algebra. Then $\Rep{\Calg}$ is a W$^*$-category with affiliated morphisms if we take $\Rep{\Calg}_\aff( (\H_1,\pi_1),(\H_2,\pi_2) )$ if we restrict to those equivalence classes which contain (unbounded) operators $T : \H_1 \to \H_2$ with dense domain $D(T) \subseteq \H_1$ which commute with the action of $\Calg$ in the sense that $u D(T) = D(T)$ and $u T = T u$ for all unitaries $u\in\Calg$.
\end{ex}
